%ID: 612083
\question Which sorting algorithm(s) perform the best given that the input array
contains only duplicates of the same number (and is therefore already sorted)? Why?

\ifprintanswers\else
\hspace \\ \\ \\ \\ \\ \\
\fi 

\begin{solution}
\textbf{Insertion sort:} $\Theta(N)$. We scan the array once and perform 0 swaps.
\\
\textbf{Heap sort:} $\Theta(N)$. Heapifying takes $\Theta(N)$ since there is no bubbling/sink-
ing to be done (the input array is already a valid max-heap). Popping $N$ elements off of the heap takes $\Theta(N)$ time for the same reason. \\
Practically, heap sort will be slower since it must first create the heap then
pop everything off the heap.
\end{solution}

\question You are given a list of first and last names. Your task is to produce a list
sorted by last name, then by first. For example, given the names 
\\ \\ 
\lstinline{"Josh Hug" "Paul Hilfinger" "John DeNero" "Dawn Song" "Hany Farid" "Dan Garcia" "Yun Song" "Bora Nikolic" "Satish Rao"}, 
\\ \\ 
you should output 
\\ \\
\lstinline{"John DeNero" "Hany Farid" "Dan Garcia" "Paul Hilfinger" "Josh Hug" "Bora Nikolic" "Satish Rao" "Dawn Song" "Yun Song"}.

\begin{parts}
\item Given a list already sorted by first name, what sorting algorithm(s)
would perform the best to complete the task? Why? 

\ifprintanswers\else
\hspace \\ \\ \\ \\ \\ \\ \\
\fi 

\begin{solution}
Since the input list is already sorted by first name, we want to run the
fastest \textbf{stable} sorting algorithm to sort the last names.
\\
Out of the comparison sorts, the fastest stable algorithm is merge sort
running in $\Theta(N \log N)$ time. Heap sort is naturally unstable as it builds the output in reverse order. While the most space efficient implementation of quicksort is unstable, it can be modified to use $\Theta(N)$ extra space to maintain stability.
\\
Because we are sorting Strings (whose characters belong to a finite
alphabet), we can use radix sorts as well. LSD and MSD radix sort are
both good candidates for the fastest algorithm. They have the same
worst-case runtimes of $\Theta(W N + W R)$ (where $W$ = length of longest
last name, $R$ = size of alphabet). MSD has a faster best-case runtime
of $\Theta(N + R)$ if all the last names have different first letters. However,
MSD would take more space due to its recursive nature.
\end{solution}

\item Again, you are given a list already sorted by first name. Suppose now you must finish sorting the list completely in-place. That is, you cannot create any additional arrays or data structures. What sorting algorithm(s) would perform the best? Why? 

\ifprintanswers\else
\hpace \\ \\ \\ \\ \\ \\ \\
\fi 

\begin{solution}
\textbf{Insertion sort:} $\Theta(N)$. We scan the array once and perform 0 swaps.
\\
Since our algorithm must take constant space, neither of our radix sorts
will work as they require external data structures to store the number of
occurrences in the alphabet. Quicksort must take up additional space
as described above in order to maintain stability. Merge sort loses
its $\Theta(N \log N)$ runtime when converted to an in-place implementation
(becoming $\Theta(N^2)$ due to the merge operation taking $\Theta(N^2)$ time).
Then, our best bet is insertion sort as it runs in $\Theta(N^2)$ time, uses
constant space, and is stable. It can, however, run faster in cases where
the list of names is already nearly sorted.
\end{solution}

\end{parts}
